### 2012-05-10 trunk/GUIErrorDetector/paper/evaluation.tex
update the num

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
However, the number of non-cyclic paths in a graph is exponential in the graph size,
and it is infeasible for this variant to enumerate all paths for a realistic
call graph, which often contains thousands of
nodes (e.g., $2^{1000}$ $\approx$ 1.07$\times$$10^{301}$). In our experiment,
we ran this variant on each subject for 1 hour, it explored 1.6$\times$$10^9$ paths on average, but did not
output any real errors before it terminated.

>>>>

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
However, the number of non-cyclic paths in a graph is exponential in the graph size,
and it is infeasible for this variant to enumerate all paths for a realistic
call graph, which often contains thousands of
nodes (e.g., $2^{1000}$ $\approx$ 1.07$\times$$10^{301}$). In our experiment,
we ran this variant on each subject for 1 hour, it explored 4.9$\times$$10^9$ paths on average, but did not
output any real errors before it terminated.
